Language Skills in an Ethnically Segmented Labour market: Estonia 1989 -- 2012

### 2018-07-20 response-to-reviewers.tex

  \begin{response}
    This is a good point.  We have added some more analysis (see
    Section 7), and it appears the story is somewhat more nuanced.
  \end{response}
\item
  \debug{OT: I'll do a rewrite after changes are made, hope it's
    sufficient.} 
  The paper needs to be checked for spelling and grammar
  errors. There are a number of typos and errors, which should be
  corrected in a revision. This would normally be a minor comment, but
  here the authors should take this comment very serious as there are
  so many mistakes.
\end{enumerate}

\subsection{Minor comments:}

\begin{enumerate}
\item- The description of the estimation models in Chapter 4 should
  be more detailed. Please describe more specifically what exactly you
  are estimating. In particular the description of the second model
  estimating the time trend is very short.

  \begin{response}
    We have improved and simplified the description of the model and related variables.
  \end{response}
  \fxwarning{ot: should you cluster if you do random effects?}
\item - The tables and figures should have notes that explain in more
  detail what is shown in the respective table and figure. For
  instance, the table notes should contain the included control
  variables, the sample period and the age restriction applied.

  \begin{response}
    We have improved the captions and notes.
  \end{response}

\item page 4: You write that you are only analysing individuals who are
working or actively looking for a job, but in line 35 on the same page
you write that inactivity is one of the included labour market
outcomes. Please clarify this and be clear in your description of what
is included in your sample.
\item 
  \debug{ot: let's make it equal (i.e. remove all observations with
    any of the variables missing.  Add a footnote that when we
    included all the variables, we still got the same results.}
\debug{SKB: I estimated the models and updated the tables with occupation added to Model 3. Added footnote linking to original tables with \enquote{unrestricted} observations}
  The sample size for different specification of the same analysis
should be the equal. Otherwise it is difficult to conclude whether the
changes in the coefficients are coming from the addition of more
controls or form the change in the size of the estimation sample.
\item 
- In the paper, you are only showing the results of the variables of
interest. I suggest to provide tables including all coefficients (not
the year dummies) in the Appendix. It might be interesting to see how
the coefficients of the control variables change across the different
models.
\debug{SKB: Will add them after I figured out how to present the results nicely formatted. It boils down to finding the right options for the \enquote{estout} or the \enquote{outtex/outreg} user provided package in Stata. I could do the formatting in Excel myself, but I prefer the Stata solution. }
\debug{SKB: I included a first try in the appendix, which is still not perfect. The labels for the variables are not existing yet or not correct. The tables are not linked yet to the main text.}
\debug{SKB: Should I include tables for unemployment as well? This would blow up the number of pages even further. I could drop the standard errors to save space. Let me know what would be best.}
\item 
- All tables: Be consistent in the description of your tables. The
table notes and the labels for e.g., "observations", are inconsistent
across the different tables. 
\debug{SKB: Fixed. Changed obs to Observations in tables}
\item
  \debug{ot: this was because of both 'B. Chiswick' and
    'B. R. Chiswick' in the bibtex file, and bibtex wanted to
    distinguish between these two guys.}
 Page 1: To cite Chiswick you are using different versions
(B. Chiswick and B. R. Chiswick).

### 2018-07-20 paper/ijm.tex
captions/notes improved

\def\tenpc{$^{\ast}$}
\def\fivepc{$^{\ast\ast}$}
\def\onepc{$^{\ast\ast\ast}$}
\newcommand{\legend}{\normalsize{Significance levels:\hspace{1em} \tenpc : 10\% \hspace{1em} \fivepc : 5\% \hspace{1em} \onepc : 1\% \normalsize}}
\def\sep{0.5em}
\def\legendTwo{\multicolumn{3}{l}{\footnotesize{Significance levels
			:\hspace{1em} $\dag$ : 10\% \hspace{1em}
			$\ast$ : 5\% \hspace{1em} $\ast\ast$ : 1\% \normalsize}}}
%SKB: Added for documenting the tables and figures
\newcommand{\modelTwo}{age, age\textsuperscript{2}, education, marriage, number of children, inter-ethnic household}
\newcommand{\modelThree}{\modelTwo, industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}
\newcommand{\modelThreeAdd}{industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}	
\newcommand{\restrictions}{The sample period is from year 2000 to year 2012. Sample is limited to persons
	25-55 year old.}
\newcommand{\agerestrictions}{25-55 year olds only.}
% Modified section numbering: removed dot at the end as this jumps
% into the cross-references.
\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}

@@

The Estonian economy, a part of the Soviet economy up to 1991, successfully
re-oriented to the Western markets and has been growing rapidly since
the mid-1990s.  \Cref{fig:gdp_growth} indicates that the Estonian economy grew around 7\% per year before the financial crisis in 2008 and after that grew at a lower rate around 3\% per year.
\fxwarning{ot: a few numbers about economic growth would be good}
\fxwarning{SKB: I added rather a figure. Pure numbers or table might not give the best impression of the growth.}
\begin{figure}[h]
	\centering
	\caption{GDP growth per year for Estonia}\label{fig:gdp_growth}
	\includegraphics[width=0.6\linewidth]{gdp_growth_per_year.eps}
	\caption*{Source: Worldbank - World Development Indicators, Series  NY.GDP.MKTP.KD.ZG}
\end{figure}
  As
a bi-product of the re-adjustment, English skills become extremely
valuable while the supply was still rather limited during the early
years of transition.

@@

% Table generated by Excel2LaTeX from sheet 'subgroups_by_ethnic_language'
\begin{sidewaystable}[tbp]
	\centering
	\caption{Averages and relative frequencies of selected explanatory
		variables 2000 -- 2012}
	\begin{tabular}{l|rrrr|rrrr}
		\toprule
		&  \multicolumn{4}{c|}{Estonians}   &   \multicolumn{4}{c}{Russians}    \\ \midrule
		Variable                    & RUS 0  & RUS 1  & ENG 0  & ENG 1  & EST 0  & EST 1  & ENG 0  & ENG 1  \\ \midrule
		Wage, men (EUR)             & 543.86 & 537.22 & 438.53 & 738.63 & 401.59 & 489.96 & 388.91 & 660.39 \\
		Wage, women (EUR)           & 345.51 & 376.98 & 301.13 & 488.83 & 238.25 & 338.62 & 266.87 & 435.60 \\
		Unemployment (\%)           & 8.74   & 7.13   & 8.83   & 4.99   & 17.30  & 11.18  & 15.06  & 11.23  \\
		EST 1 (\%)                  & 99.97  & 99.58  & 99.50  & 99.95  & 0.00   & 100.00 & 40.84  & 80.97  \\
		RUS 1 (\%)                  & 0.00   & 100.00 & 77.35  & 82.86  & 99.90  & 99.04  & 99.65  & 98.77  \\
		ENG 1 (\%)                  & 29.47  & 37.16  & 0.00   & 100.00 & 6.70   & 30.69  & 0.00   & 100.00 \\
		College Degree (\%)         & 15.61  & 23.44  & 10.77  & 41.38  & 12.66  & 28.64  & 13.93  & 49.16  \\
		Married (\%)                & 40.09  & 55.71  & 54.11  & 49.53  & 63.54  & 60.78  & 63.38  & 56.99  \\
		Inter-ethnic household (\%) & 1.34   & 5.20   & 4.79   & 3.70   & 5.07   & 19.46  & 11.97  & 12.17  \\
		Age                         & 37.05  & 41.83  & 42.39  & 38.05  & 42.14  & 40.54  & 42.15  & 37.83  \\
		Kids (number)               & 1.08   & 1.00   & 1.00   & 1.00   & 0.71   & 0.76   & 0.75   & 0.68   \\
		\textbf{Residence County }  &        &        &        &        &        &        &        &        \\
		Metropolitan (\%)           & 17.74  & 22.58  & 14.03  & 35.25  & 35.43  & 56.37  & 38.82  & 75.50  \\
		North-East (\%)             & 0.64   & 3.14   & 3.46   & 1.10   & 53.84  & 15.85  & 40.90  & 11.54  \\
		\textbf{Workplace}          &        &        &        &        &        &        &        &        \\
		Tenure (years)              & 6.17   & 7.33   & 7.45   & 6.40   & 8.19   & 7.23   & 8.08   & 5.99   \\
		Public sector (\%)          & 20.03  & 24.81  & 21.79  & 27.55  & 11.62  & 21.67  & 16.28  & 18.14  \\
		Primary sector (\%)         & 14.10  & 9.80   & 13.00  & 6.43   & 9.91   & 7.46   & 8.82   & 8.11   \\
		Secondary sector (\%)       & 31.02  & 27.20  & 32.63  & 19.41  & 47.21  & 29.72  & 41.54  & 24.07  \\
		Tertiary sector (\%)        & 26.17  & 30.12  & 26.52  & 34.46  & 27.17  & 33.96  & 28.37  & 40.96  \\
		\# Observations             & 14,943 & 57,270 & 46,525 & 25,688 & 13,805 & 12,830 & 21,773 & 4,862  \\ \bottomrule
	\end{tabular}%
	\label{tab:descriptive}%
	\caption*{\small
		Workplace--related variables are reported for employed individuals,
		other variables for the complete workforce.  Sample is limited to persons
		25-55 year old.\\
		\emph{RUS 0} refers to individuals who cannot speak Russian and
		\emph{RUS 1} to those who can. Analogously for English
                (ENG) and
		Estonian (EST).\\
		Primary sector = Agriculture,
		Fishing, Mining \\ Secondary sector = Manufacturing,
		Construction, Electricity \\ Tertiary (service) sector =
		Wholesale, Hotels, Transport, Financial intermediation, Real
		estate \\ Public sector = Public administration, Education,
		Health}
\end{sidewaystable}%

@@

\begin{table}[h]
	\begin{center}
		\caption{Estimation results for unemployment.}
		\label{tab:unemployment_estimation_by_sex_and_ethnic_same_sample} %SKB 04.07.2018 14:22:Not yet updated only prepared
		\begin{tabular}{l D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad\qquad}
				D{.}{.}{3} @{\qquad} D{.}{.}{3}}
			\toprule
			&         \multicolumn{2}{c}{Men}         &        \multicolumn{2}{c}{Women}        \\
			Estonians:      & \multicolumn{1}{c}{1}      & \multicolumn{1}{l}{\hspace{10pt}2} & \multicolumn{1}{c}{1}      & \multicolumn{1}{c}{2}      \\
			Russian         & -0.026^{***}               & -0.001                             & -0.009^{*}                 & 0.010^{**}                 \\
			                & (0.006)                    & (0.006)                            & (0.005)                    & (0.005)                    \\
			English         & -0.047^{***}               & -0.019^{***}                       & -0.024^{***}               & -0.008^{*}                 \\
			                & (0.004)                    & (0.005)                            & (0.004)                    & (0.004)                    \\
			\# Observations          & \multicolumn{1}{c}{36,132} & \multicolumn{1}{l}{36,132}         & \multicolumn{1}{l}{36,015} & \multicolumn{1}{c}{36,015} \\
			$R^{2}$         & 0.022                      & 0.047                              & 0.012                      & 0.036                      \\ \hline
			Russians: & \\
			Estonian        & -0.052^{***}               & -0.052^{***}                       & -0.065^{***}               & -0.045^{***}               \\
			                & (0.010)                    & (0.011)                            & (0.009)                    & (0.010)                    \\
			English         & -0.020                     & 0.006                              & -0.014                     & -0.003                     \\
			                & (0.012)                    & (0.014)                            & (0.011)                    & (0.012)                    \\
			\# Observations          & \multicolumn{1}{c}{12,942} & \multicolumn{1}{l}{12,942}         & \multicolumn{1}{l}{13,674} & \multicolumn{1}{c}{13,674} \\
			$R^{2}$         & 0.033                      & 0.066                              & 0.023                      & 0.043                      \\ \hline
			year dummies    & \V                         & \V                                 & \V                         & \V                         \\
			indiv. charact. &                            & \V                                 &                            & \V                         \\
			\bottomrule
		\end{tabular}%
		\begin{flushleft}
			\caption*{ \legend \\ Standard errors (clustered on individuals) in parentheses.\\  Individual characteristics are \modelTwo. \\ \restrictions}
		\end{flushleft}
	\end{center}

@@

			\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis \\ Individual characteristics are \modelTwo. \\ Workplace characteristics are \modelThreeAdd. \\ \restrictions}

@@

\begin{table}[htbp]
	\centering
	\caption{The trend over time across the age groups (ethnic Estonians)}
	\begin{tabular}{lccc|cc c}
          \toprule
		\multicolumn{7}{l}{Estonian speakers. Dependent variable: log wage}          \\ \hline
		Russian:   &    \multicolumn{3}{c|}{Men}    &   \multicolumn{3}{c}{Women}    \\
		years/age: & 25-35    & 36-45    & 46-55    & 25-35    & 36-45    & 46-55    \\ \midrule
		89-95      & 0.064    & 0.247*** & 0.187*** & 0.117*   & 0.033    & 0.058    \\
		           & (0.069)  & (0.068)  & (0.064)  & (0.053)  & (0.057)  & (0.056)  \\
		96-99      & 0.116**  & 0.161**  & 0.190*** & 0.059*   & 0.114*** & 0.131*** \\
		           & (0.042)  & (0.049)  & (0.054)  & (0.030)  & (0.030)  & (0.033)  \\
		00-07      & 0.054*   & 0.157*** & 0.093*   & 0.041    & 0.022    & 0.042    \\
		           & (0.026)  & (0.037)  & (0.037)  & (0.024)  & (0.021)  & (0.026)  \\
		08-12      & 0.041    & 0.032    & 0.088    & 0.032    & 0.012    & 0.061    \\
		           & (0.032)  & (0.049)  & (0.069)  & (0.030)  & (0.026)  & (0.033)  \\ \hline
		English:   &          &          &          &          &          &          \\
		89-95      & 0.097    & -0.008   & 0.066    & 0.070    & 0.042    & 0.101    \\
		           & (0.064)  & (0.065)  & (0.083)  & (0.049)  & (0.048)  & (0.078)  \\
		96-99      & 0.190*** & 0.276*** & 0.137*   & 0.113*** & 0.101*** & 0.101**  \\
		           & (0.036)  & (0.049)  & (0.054)  & (0.031)  & (0.028)  & (0.038)  \\
		00-07      & 0.166*** & 0.158*** & 0.225*** & 0.159*** & 0.073*** & 0.164*** \\
		           & (0.027)  & (0.036)  & (0.041)  & (0.024)  & (0.021)  & (0.025)  \\
		08-12      & 0.088*   & 0.179*** & 0.236*** & 0.166*** & 0.123*** & 0.145*** \\
		           & (0.039)  & (0.035)  & (0.043)  & (0.037)  & (0.024)  & (0.029)  \\ 
          \midrule
		\multicolumn{7}{l}{Russian speakers. Dependent variable: log wage}\\
		\midrule
		Estonian:&\multicolumn{3}{c|}{Men} &\multicolumn{3}{c}{Women}\\
		years/age: & 25-35   & 36-45    & 46-55   & 25-35   & 36-45   & 46-55    \\
		\midrule
		89-95      & -0.027  & -0.113   & -0.029  & 0.134*  & 0.073   & -0.039   \\
		           & (0.094) & (0.077)  & (0.079) & (0.056) & (0.052) & (0.059)  \\
		96-99      & -0.023  & 0.001    & 0.049   & 0.049   & 0.034   & 0.071    \\
		           & (0.050) & (0.048)  & (0.060) & (0.045) & (0.035) & (0.037)  \\
		00-07      & -0.038  & -0.034   & 0.042   & 0.099** & 0.089** & 0.122*** \\
		           & (0.038) & (0.049)  & (0.043) & (0.033) & (0.031) & (0.028)  \\
		08-12      & -0.004  & -0.034   & 0.002   & 0.145** & 0.123** & 0.103**  \\
		           & (0.055) & (0.050)  & (0.047) & (0.051) & (0.044) & (0.038)  \\ \midrule
		English:   &         &          &         &         &         &          \\
		89-95      & 0.325*  & 0.362*   & 0.473*  & 0.191   & 0.096   & -0.096   \\
		           & (0.160) & (0.151)  & (0.216) & (0.104) & (0.085) & (0.353)  \\
		96-99      & 0.324** & 0.224*   & 0.129   & 0.241** & 0.048   & 0.281*   \\
		           & (0.101) & (0.103)  & (0.132) & (0.078) & (0.091) & (0.120)  \\
		00-07      & 0.142** & 0.107    & 0.169*  & 0.127** & 0.104   & 0.127*   \\
		           & (0.051) & (0.097)  & (0.072) & (0.049) & (0.060) & (0.057)  \\
		08-12      & 0.140*  & 0.212*** & 0.138   & 0.029   & 0.105*  & 0.040    \\
		           & (0.056) & (0.057)  & (0.072) & (0.049) & (0.050) & (0.055)  \\
		\bottomrule
	\end{tabular}

	\caption*{\legend \\ Standard errors (clustered on individuals) in parenthesis}
	\label{tab:age_group_trend}
\end{table}

@@

\begin{table}[t]
	\centering
	\caption{Language environment and language need at workplace}
	\label{tab:environment_descriptive}
	\begin{tabular}{lrr}
		\toprule
		                                     & men  & women \\
		\midrule
		main communication language Estonian & 15.0 & 22.2  \\
		Need Estonian at work                & 53.0 & 61.9  \\
		Need English  at work                & 26.5 & 11.9  \\
		\midrule
		observations                         & 132  & 134   \\
		\bottomrule
	\end{tabular}
	\begin{flushleft}
		Note: percentage of respondents who respond affirmatively
	\end{flushleft}
\end{table}

>>>>

\def\tenpc{$^{\ast}$}
\def\fivepc{$^{\ast\ast}$}
\def\onepc{$^{\ast\ast\ast}$}
\newcommand{\legend}{\normalsize{Significance levels:\hspace{1em} \tenpc : 10\% \hspace{1em} \fivepc : 5\% \hspace{1em} \onepc : 1\% \normalsize}}
\def\sep{0.5em}
\def\legendTwo{\multicolumn{3}{l}{\footnotesize{Significance levels
			:\hspace{1em} $\dag$ : 10\% \hspace{1em}
			$\ast$ : 5\% \hspace{1em} $\ast\ast$ : 1\% \normalsize}}}
%SKB: Added for documenting the tables and figures
\newcommand{\modelTwo}{age, age\textsuperscript{2}, education, marriage, number of children, inter-ethnic household}
\newcommand{\modelThree}{\modelTwo, industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}
\newcommand{\modelThreeAdd}{industry, occupation, ownership type of company, number of workers in company, working in the public sector, experience in company}	
\newcommand{\restrictions}{Only years 2000--2012 and individuals 25-55
  year old included in the sample.}
\newcommand{\agerestrictions}{25-55 year olds only.}
% Modified section numbering: removed dot at the end as this jumps
% into the cross-references.
\renewcommand{\thesection}{\arabic{section}}
\renewcommand{\thesubsection}{\thesection.\arabic{subsection}}

@@

The Estonian economy, a part of the Soviet economy up to 1991, successfully
re-oriented to the Western markets and has been growing rapidly since
the mid-1990s.  \Cref{fig:gdp_growth} indicates that the Estonian economy grew around 7\% per year before the financial crisis in 2008 and after that grew at a lower rate around 3\% per year.
\begin{figure}[h]
	\centering
	\caption{Annual GDP growth in Estonia}\label{fig:gdp_growth}
	\includegraphics[width=0.6\linewidth]{gdp_growth_per_year.eps}
	\caption*{Source: Worldbank - World Development Indicators, Series  NY.GDP.MKTP.KD.ZG}
\end{figure}
\fxnote{ot: remove the cryptic series?}
  As
a bi-product of the re-adjustment, English skills become extremely
valuable while the supply was still rather limited during the early
years of transition.

@@

% Table generated by Excel2LaTeX from sheet 'subgroups_by_ethnic_language'
\begin{sidewaystable}[tbp]
	\centering
	\caption{Averages and relative frequencies of selected explanatory
		variables 2000 -- 2012}
	\begin{tabular}{l|rrrr|rrrr}
		\toprule
		&  \multicolumn{4}{c|}{Estonians}   &   \multicolumn{4}{c}{Russians}    \\ \midrule
		Variable                    & RUS 0  & RUS 1  & ENG 0  & ENG 1  & EST 0  & EST 1  & ENG 0  & ENG 1  \\ \midrule
		Wage, men (EUR)             & 543.86 & 537.22 & 438.53 & 738.63 & 401.59 & 489.96 & 388.91 & 660.39 \\
		Wage, women (EUR)           & 345.51 & 376.98 & 301.13 & 488.83 & 238.25 & 338.62 & 266.87 & 435.60 \\
		Unemployment (\%)           & 8.74   & 7.13   & 8.83   & 4.99   & 17.30  & 11.18  & 15.06  & 11.23  \\
		EST 1 (\%)                  & 99.97  & 99.58  & 99.50  & 99.95  & 0.00   & 100.00 & 40.84  & 80.97  \\
		RUS 1 (\%)                  & 0.00   & 100.00 & 77.35  & 82.86  & 99.90  & 99.04  & 99.65  & 98.77  \\
		ENG 1 (\%)                  & 29.47  & 37.16  & 0.00   & 100.00 & 6.70   & 30.69  & 0.00   & 100.00 \\
		College Degree (\%)         & 15.61  & 23.44  & 10.77  & 41.38  & 12.66  & 28.64  & 13.93  & 49.16  \\
		Married (\%)                & 40.09  & 55.71  & 54.11  & 49.53  & 63.54  & 60.78  & 63.38  & 56.99  \\
		Inter-ethnic household (\%) & 1.34   & 5.20   & 4.79   & 3.70   & 5.07   & 19.46  & 11.97  & 12.17  \\
		Age                         & 37.05  & 41.83  & 42.39  & 38.05  & 42.14  & 40.54  & 42.15  & 37.83  \\
		Kids (number)               & 1.08   & 1.00   & 1.00   & 1.00   & 0.71   & 0.76   & 0.75   & 0.68   \\
		\textbf{Residence County }  &        &        &        &        &        &        &        &        \\
		Metropolitan (\%)           & 17.74  & 22.58  & 14.03  & 35.25  & 35.43  & 56.37  & 38.82  & 75.50  \\
		North-East (\%)             & 0.64   & 3.14   & 3.46   & 1.10   & 53.84  & 15.85  & 40.90  & 11.54  \\
		\textbf{Workplace}          &        &        &        &        &        &        &        &        \\
		Tenure (years)              & 6.17   & 7.33   & 7.45   & 6.40   & 8.19   & 7.23   & 8.08   & 5.99   \\
		Public sector (\%)          & 20.03  & 24.81  & 21.79  & 27.55  & 11.62  & 21.67  & 16.28  & 18.14  \\
		Primary sector (\%)         & 14.10  & 9.80   & 13.00  & 6.43   & 9.91   & 7.46   & 8.82   & 8.11   \\
		Secondary sector (\%)       & 31.02  & 27.20  & 32.63  & 19.41  & 47.21  & 29.72  & 41.54  & 24.07  \\
		Tertiary sector (\%)        & 26.17  & 30.12  & 26.52  & 34.46  & 27.17  & 33.96  & 28.37  & 40.96  \\
		\# Observations             & 14,943 & 57,270 & 46,525 & 25,688 & 13,805 & 12,830 & 21,773 & 4,862  \\ \bottomrule
	\end{tabular}%
	\label{tab:descriptive}%
        \newgeometry{textwidth=0.75\paperheight}
        \begin{flushleft}
          \small Workplace--related variables are reported for
          employed individuals, other variables for the complete
          workforce.  Sample is limited to persons
          25-55 year old.\\
          \emph{RUS 0} refers to individuals who cannot speak
          Russian and \emph{RUS 1} to those who can. Analogously for
          English (ENG) and
          Estonian (EST).\\
          Primary sector = Agriculture, Fishing, Mining; Secondary
          sector = Manufacturing, Construction, Electricity;
          Tertiary (service) sector = Wholesale, Hotels, Transport,
          Financial intermediation, Real estate; Public sector =
          Public administration, Education, Health
        \end{flushleft}
\end{sidewaystable}%

@@

\begin{table}[h]
	\begin{center}
		\caption{Estimation results for unemployment probability.}
		\label{tab:unemployment_estimation_by_sex_and_ethnic_same_sample} %SKB 04.07.2018 14:22:Not yet updated only prepared
		\begin{tabular}{l D{.}{.}{3} @{\qquad} D{.}{.}{3} @{\qquad\qquad}
				D{.}{.}{3} @{\qquad} D{.}{.}{3}}
			\toprule
			&         \multicolumn{2}{c}{Men}         &        \multicolumn{2}{c}{Women}        \\
			Estonians:      & \multicolumn{1}{c}{1}      & \multicolumn{1}{l}{\hspace{10pt}2} & \multicolumn{1}{c}{1}      & \multicolumn{1}{c}{2}      \\
			Russian         & -0.026^{***}               & -0.001                             & -0.009^{*}                 & 0.010^{**}                 \\
			                & (0.006)                    & (0.006)                            & (0.005)                    & (0.005)                    \\
			English         & -0.047^{***}               & -0.019^{***}                       & -0.024^{***}               & -0.008^{*}                 \\
			                & (0.004)                    & (0.005)                            & (0.004)                    & (0.004)                    \\
			\# Observations          & \multicolumn{1}{c}{36,132} & \multicolumn{1}{l}{36,132}         & \multicolumn{1}{l}{36,015} & \multicolumn{1}{c}{36,015} \\
			$R^{2}$         & 0.022                      & 0.047                              & 0.012                      & 0.036                      \\ \hline
			Russians: & \\
			Estonian        & -0.052^{***}               & -0.052^{***}                       & -0.065^{***}               & -0.045^{***}               \\
			                & (0.010)                    & (0.011)                            & (0.009)                    & (0.010)                    \\
			English         & -0.020                     & 0.006                              & -0.014                     & -0.003                     \\
			                & (0.012)                    & (0.014)                            & (0.011)                    & (0.012)                    \\
			\# Observations          & \multicolumn{1}{c}{12,942} & \multicolumn{1}{l}{12,942}         & \multicolumn{1}{l}{13,674} & \multicolumn{1}{c}{13,674} \\
			$R^{2}$         & 0.033                      & 0.066                              & 0.023                      & 0.043                      \\ \hline
			year dummies    & \V                         & \V                                 & \V                         & \V                         \\
			indiv. charact. &                            & \V                                 &                            & \V                         \\
			\bottomrule
		\end{tabular}%
		\begin{flushleft}
                  \legend \\ Standard errors (clustered on individuals) in parentheses.\\  Individual characteristics are \modelTwo. \\ \restrictions
		\end{flushleft}
	\end{center}

@@

                  \legend \\ Standard errors (clustered on individuals) in parenthesis \\ Individual characteristics are \modelTwo. \\ Workplace characteristics are \modelThreeAdd. \\ \restrictions

@@

\begin{table}[htbp]
	\centering
	\caption{Estimated trend over time across the age groups}
	\begin{tabular}{lccc|cc c}
          \toprule
		\multicolumn{7}{l}{Estonian speakers. Dependent variable: log wage}          \\ \hline
		Russian:   &    \multicolumn{3}{c|}{Men}    &   \multicolumn{3}{c}{Women}    \\
		years/age: & 25-35    & 36-45    & 46-55    & 25-35    & 36-45    & 46-55    \\ \midrule
		89-95      & 0.064    & 0.247*** & 0.187*** & 0.117*   & 0.033    & 0.058    \\
		           & (0.069)  & (0.068)  & (0.064)  & (0.053)  & (0.057)  & (0.056)  \\
		96-99      & 0.116**  & 0.161**  & 0.190*** & 0.059*   & 0.114*** & 0.131*** \\
		           & (0.042)  & (0.049)  & (0.054)  & (0.030)  & (0.030)  & (0.033)  \\
		00-07      & 0.054*   & 0.157*** & 0.093*   & 0.041    & 0.022    & 0.042    \\
		           & (0.026)  & (0.037)  & (0.037)  & (0.024)  & (0.021)  & (0.026)  \\
		08-12      & 0.041    & 0.032    & 0.088    & 0.032    & 0.012    & 0.061    \\
		           & (0.032)  & (0.049)  & (0.069)  & (0.030)  & (0.026)  & (0.033)  \\ \hline
		English:   &          &          &          &          &          &          \\
		89-95      & 0.097    & -0.008   & 0.066    & 0.070    & 0.042    & 0.101    \\
		           & (0.064)  & (0.065)  & (0.083)  & (0.049)  & (0.048)  & (0.078)  \\
		96-99      & 0.190*** & 0.276*** & 0.137*   & 0.113*** & 0.101*** & 0.101**  \\
		           & (0.036)  & (0.049)  & (0.054)  & (0.031)  & (0.028)  & (0.038)  \\
		00-07      & 0.166*** & 0.158*** & 0.225*** & 0.159*** & 0.073*** & 0.164*** \\
		           & (0.027)  & (0.036)  & (0.041)  & (0.024)  & (0.021)  & (0.025)  \\
		08-12      & 0.088*   & 0.179*** & 0.236*** & 0.166*** & 0.123*** & 0.145*** \\
		           & (0.039)  & (0.035)  & (0.043)  & (0.037)  & (0.024)  & (0.029)  \\ 
          \midrule
		\multicolumn{7}{l}{Russian speakers. Dependent variable: log wage}\\
		\midrule
		Estonian:&\multicolumn{3}{c|}{Men} &\multicolumn{3}{c}{Women}\\
		years/age: & 25-35   & 36-45    & 46-55   & 25-35   & 36-45   & 46-55    \\
		\midrule
		89-95      & -0.027  & -0.113   & -0.029  & 0.134*  & 0.073   & -0.039   \\
		           & (0.094) & (0.077)  & (0.079) & (0.056) & (0.052) & (0.059)  \\
		96-99      & -0.023  & 0.001    & 0.049   & 0.049   & 0.034   & 0.071    \\
		           & (0.050) & (0.048)  & (0.060) & (0.045) & (0.035) & (0.037)  \\
		00-07      & -0.038  & -0.034   & 0.042   & 0.099** & 0.089** & 0.122*** \\
		           & (0.038) & (0.049)  & (0.043) & (0.033) & (0.031) & (0.028)  \\
		08-12      & -0.004  & -0.034   & 0.002   & 0.145** & 0.123** & 0.103**  \\
		           & (0.055) & (0.050)  & (0.047) & (0.051) & (0.044) & (0.038)  \\ \midrule
		English:   &         &          &         &         &         &          \\
		89-95      & 0.325*  & 0.362*   & 0.473*  & 0.191   & 0.096   & -0.096   \\
		           & (0.160) & (0.151)  & (0.216) & (0.104) & (0.085) & (0.353)  \\
		96-99      & 0.324** & 0.224*   & 0.129   & 0.241** & 0.048   & 0.281*   \\
		           & (0.101) & (0.103)  & (0.132) & (0.078) & (0.091) & (0.120)  \\
		00-07      & 0.142** & 0.107    & 0.169*  & 0.127** & 0.104   & 0.127*   \\
		           & (0.051) & (0.097)  & (0.072) & (0.049) & (0.060) & (0.057)  \\
		08-12      & 0.140*  & 0.212*** & 0.138   & 0.029   & 0.105*  & 0.040    \\
		           & (0.056) & (0.057)  & (0.072) & (0.049) & (0.050) & (0.055)  \\
		\bottomrule
	\end{tabular}
        \begin{flushleft}
          \legend \\ Standard errors (clustered on individuals) in
          parenthesis \\
          Individual characteristics are \modelTwo. \\
          \restrictions
        \end{flushleft}
	\label{tab:age_group_trend}
\end{table}

@@

\begin{table}[t]
	\centering
	\caption{Language environment and language need at workplace}
	\label{tab:environment_descriptive}
	\begin{tabular}{lrr}
		\toprule
		                                     & men  & women \\
		\midrule
		main communication language Estonian & 15.0 & 22.2  \\
		Need Estonian at work                & 53.0 & 61.9  \\
		Need English  at work                & 26.5 & 11.9  \\
		\midrule
		observations                         & 132  & 134   \\
		\bottomrule
	\end{tabular}
	\begin{flushleft}
		Note: percentage of respondents (Russian speakers) who respond affirmatively
	\end{flushleft}
\end{table}
